Biology background

### 2015-04-12 Rmarkdown/biology_background.Rmd
Add chapter abstract macro

\section{Chapter overview}\label{sec:biology_background_chapter_overview}

In this chapter I summarise the basic biology necessary for
understanding my thesis. I introduce DNA methylation, describe some of its biological roles, and introduce assays for studying DNA methylation, with a particular focus on bisulfite-sequencing.

@@

Genomics research was revolutionised by the development of cheap high-throughput sequencing technology, and the study of DNA methylation was no exception. In 2008, two papers were published describing methods for whole-genome shotgun sequencing of bisulfite-converted DNA using the nascent Illumina sequencing technology \citep{Cokus:2008fc, Lister:2008bh}. Whole-genome bisulfite-sequencing remains the gold standard assay for measuring genome-wide DNA methylation data.

>>>>

\begin{chapabstract}
I summarise the basic biology necessary for understanding my thesis. I introduce DNA methylation, describe some of its biological roles, and introduce assays for studying DNA methylation, with a particular focus on bisulfite-sequencing.
\begin{end}

@@

Genomics research was revolutionised by the development of cheap high-throughput sequencing technology, and the study of DNA methylation was no exception. In 2008, two papers were published describing methods for whole-genome shotgun sequencing of bisulfite-converted DNA using the nascent Solexa/Illumina sequencing technology \citep{Cokus:2008fc, Lister:2008bh}. Whole-genome bisulfite-sequencing remains the gold standard assay for measuring genome-wide DNA methylation data.
